Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-21 ch02-qlogms/excitation-design.tex
Changes all over the place
Some uniformity stuff
LRM: part of bias, some intro
Uniform commands: part 1

\chapter{Design of excitation signals}
\label{sec:excitation}
\def\thisDir{ch02-qlogms}
\tikzsetfigurename{ch02fig}
\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM, }

@@

In open loop experiments, the scaled average information matrix is given by
\begin{align}
\IF & = \lim_{N\rightarrow\infty}
          \frac{1}{N}
            \sum_{t=1}^{N}
              {\left(\frac{\partial\hat{y}(t)}{\partial\theta}\right)
               \left(\frac{\partial\hat{y}(t)}{\partial\theta}\right)^{\T}},\\
\frac{\partial\hat{y}(t)}{\partial\theta}
    & =\frac{\partial G(s,\theta)}{\partial \theta}u(t).
\end{align}
By Parseval's theorem, $\IF$ can be expressed as
\begin{align}
\IF &= \frac{1}{\pi}
         \int\limits_0^\infty \RealPart
           \left\{      \frac{\partial G(j\omega)}{\partial \theta}
                  \left[\frac{\partial G(j\omega)}{\partial \theta}\right]^{\HT}
           \right\}
           \powerspec{u}(j\omega)
           \dd{\omega} \text{.}
\label{eq:excitation:IF}
\end{align}
The information matrix is a function of the input power spectrum $\powerspec{u}$, which is the only entity that can be used to improve the quality of the estimates. 
A common optimality criterion is D-optimality where $\det{\IF}$ is maximized~\citep{Goodwin1977}.

@@

The information matrix tells us how good the individual parameter estimates are. However, if we are interested in estimating a transfer function $G(s,\theta)$ the quality of this estimate is of more importance. 
It is possible to find an expression for the variance of $\hat{G}(j\omega,\theta)$ using the Gauss approximation formula \citep{Ljung1999, Pintelon2012}. This gives
\begin{align}
\var{\hat{G}(j\omega)} &\approx \frac{\partial G^H(j\omega)}{\partial \theta}\IF^{-1}\frac{\partial G(j\omega)}{\partial \theta}.
\label{eq:excitation:varG}
\end{align}

@@

The information matrix for systems of the type \eqref{eq:excitation:sumSys} will have a block structure commensurate with the dimension of $\theta_i$ given by
\begin{align}
\IF &= \frac{1}{\pi}
\begin{bmatrix}
  \partial G_{1,1}        &\partial G_{1,2}       &\deemph{\cdots}         &\partial G_{1,K}\\
  \partial G_{2,1}        &\partial G_{2,2}       &\deemph{\cdots}         &\partial G_{2,K}\\
  \deemph{\vdots}                  &\deemph{\vdots}                 &\deemph{\ddots}         &\deemph{\vdots}          \\
  \partial G_{K,1}        &\partial G_{K,2}       &\deemph{\cdots}         &\partial G_{K,K}
\end{bmatrix},\\
\partial G_{i,j} &= \int_0^\infty
                      \RealPart\left\{
                          \frac{\partial G_i}
                               {\partial \theta_i}
                          \frac{\partial G_j^{\HT}}
                               {\partial \theta_j}
                                \right\}
                      \phi_u(\omega)\dd\omega.
\end{align}

@@

\subsubsection{Example: Sum of two second-order systems}
\label{sec:excitation:ex:sumOfSecondOrderSipmle}
Consider the system
\begin{align}
G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)%\\
%&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping[1]}{\wn[1]}s + 1} + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\\damping[2]}{\wn[2]}s + 1},
\end{align}
with $\theta_1=[\wn[1]\;\damping[1]]^{\T}$ and $\theta_2=[\wn[2]\;\damping[2]]^{\T}$.
The information matrix for this system is
\begin{align}
\IF &=
       \begin{bmatrix}
         \partial G_{1,1}  & \partial G_{1,2}\\
         \partial G_{2,1}  & \partial G_{2,2}
       \end{bmatrix}.
\label{eq:excitation:infoEx}
\end{align}
To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:excitation:infoEx}, when the input spectrum \eqref{eq:excitation:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.

@@

In \figref{fig:excitation:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations. It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well-separated increases the decoupling. 
The diagonal blocks of the normalized $\IF$ in all cases have some elements close to $1$. 
In this example, the $\damping$ is set to be the same in both sub-systems. 
Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.

Based on the above arguments, we approximate the information matrix for lightly-damped systems as a block-diagonal matrix:
\begin{align}
\IF&\approx \begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
                        \deemph{0}&\partial G_{2,2}\end{bmatrix}.
\end{align}
Hence the variance of the estimate $\hat{G}(s,\theta)$ becomes
\begin{align}
\var{\hat{G}(\omega)} &\approx \frac{\partial G^{\HT}(e^{j\omega})}{\partial \theta}\begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
                        \deemph{0}&\partial G_{2,2}\end{bmatrix}^{-1}\frac{\partial G(e^{j\omega})}{\partial \theta}\\
&=\var{\hat{G}_1(\omega)} + \var{\hat{G}_2(\omega)}.
\end{align}

@@

  Using this extension, the frequency range covered by $f_k$ can then be calculated as
    \begin{align}
      \fMin{k} &= \mean{f_{k-1}}{f_k}\\
      \fMax{k} &= \mean{f_{k+1}}{f_k}
    \label{eq:excitation:fRange}
    \text{.}
    \end{align}
  This range can be seen as the power-spectral density counterpart of the discrete spectrum relation \eqref{eq:excitation:nearestLines}.
  Consequently, both signals can be expected to behave in approximately the same way.

@@

\section{Simulations} \label{sec:excitation:simulation}
In the following set of simulations, we will study how the \gls{FRF} of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from \secref{sec:excitation:multisine}.
  \subsection{Setup}
  We consider second-order systems with an equal damping and with resonance frequencies $4$, $8$, $20$, $40$, $80$, $200$, $400$, $800$, $2000$ and $4000 \unit{Hz}$.
  Using the \matlab\ instruction \texttt{cheby1}, discrete-time equivalents of these systems are generated.
  These can be represented by a transfer function of the form:
  \begin{equation}
    G \left( z \right)\Big|_{\damping, \fR} =
       \frac{         b_2  z^{2} + b_1 z + b_0}%
            {\phantom{a_2} z^{2} + a_1 z + a_0}
  \text{.}
  \label{eq:excitation:secondOrderSystemDTidentifiable}
  \end{equation}

>>>>

\chapter{Design of Excitation Signals}
\label{sec:excitation}
\def\thisDir{ch02-qlogms}
\tikzsetfigurename{ch02fig}
\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM, }

@@

In open loop experiments, the scaled average information matrix is given by
\begin{align}
\Fi{\theta} & = \lim_{N\rightarrow\infty}
          \frac{1}{N}
            \sum_{t=1}^{N}
              {\left(\frac{\partial\hat{y}(t)}{\partial\theta}\right)
               \left(\frac{\partial\hat{y}(t)}{\partial\theta}\right)^{\T}},\\
\frac{\partial\hat{y}(t)}{\partial\theta}
    & =\frac{\partial G(s,\theta)}{\partial \theta}u(t).
\end{align}
By Parseval's theorem, $\Fi{\theta}$ can be expressed as
\begin{align}
\Fi{\theta} &= \frac{1}{\pi}
         \int\limits_0^\infty \RealPart
           \left\{      \frac{\partial G(j\omega)}{\partial \theta}
                  \left[\frac{\partial G(j\omega)}{\partial \theta}\right]^{\HT}
           \right\}
           \powerspec{u}(j\omega)
           \dd{\omega} \text{.}
\label{eq:excitation:IF}
\end{align}
The information matrix is a function of the input power spectrum $\powerspec{u}$, which is the only entity that can be used to improve the quality of the estimates. 
A common optimality criterion is D-optimality where $\det{\Fi{\theta}}$ is maximized~\citep{Goodwin1977}.

@@

The information matrix tells us how good the individual parameter estimates are. However, if we are interested in estimating a transfer function $G(s,\theta)$ the quality of this estimate is of more importance. 
It is possible to find an expression for the variance of $\hat{G}(j\omega,\theta)$ using the Gauss approximation formula \citep{Ljung1999, Pintelon2012}. This gives
\begin{align}
\var{\hat{G}(j\omega)} &\approx \frac{\partial G^H(j\omega)}{\partial \theta}\Fi{\theta}^{-1}\frac{\partial G(j\omega)}{\partial \theta}.
\label{eq:excitation:varG}
\end{align}

@@

The information matrix for systems of the type \eqref{eq:excitation:sumSys} will have a block structure commensurate with the dimension of $\theta_i$ given by
\begin{align}
\Fi{\theta} &= \frac{1}{\pi}
\begin{bmatrix}
  \partial G_{1,1}        &\partial G_{1,2}       &\deemph{\cdots}         &\partial G_{1,K}\\
  \partial G_{2,1}        &\partial G_{2,2}       &\deemph{\cdots}         &\partial G_{2,K}\\
  \deemph{\vdots}                  &\deemph{\vdots}                 &\deemph{\ddots}         &\deemph{\vdots}          \\
  \partial G_{K,1}        &\partial G_{K,2}       &\deemph{\cdots}         &\partial G_{K,K}
\end{bmatrix},\\
\partial G_{i,j} &= \int_0^\infty
                      \RealPart\left\{
                          \frac{\partial G_i}
                               {\partial \theta_i}
                          \frac{\partial G_j^{\HT}}
                               {\partial \theta_j}
                                \right\}
                      \phi_u(\omega)\dd\omega.
\end{align}

@@

\subsubsection{Example: Sum of two second-order systems}
\label{sec:excitation:ex:sumOfSecondOrderSipmle}
Consider the system
\begin{align}
G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)%\\
%&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping[1]}{\wn[1]}s + 1} + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\\damping[2]}{\wn[2]}s + 1},
\end{align}
with $\theta_1=[\wn[1]\;\damping[1]]^{\T}$ and $\theta_2=[\wn[2]\;\damping[2]]^{\T}$.
The information matrix for this system is
\begin{align}
\Fi{\theta} &=
       \begin{bmatrix}
         \partial G_{1,1}  & \partial G_{1,2}\\
         \partial G_{2,1}  & \partial G_{2,2}
       \end{bmatrix}.
\label{eq:excitation:infoEx}
\end{align}
To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:excitation:infoEx}, when the input spectrum \eqref{eq:excitation:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.

@@

In \figref{fig:excitation:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations. It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well-separated increases the decoupling. 
The diagonal blocks of the normalized $\Fi{\theta}$ in all cases have some elements close to $1$. 
In this example, the $\damping$ is set to be the same in both sub-systems. 
Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.

Based on the above arguments, we approximate the information matrix for lightly-damped systems as a block-diagonal matrix:
\begin{align}
\Fi{\theta}&\approx \begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
                        \deemph{0}&\partial G_{2,2}\end{bmatrix}.
\end{align}
Hence the variance of the estimate $\hat{G}(s,\theta)$ becomes
\begin{align}
\var{\hat{G}(\omega)} &\approx \frac{\partial G^{\HT}(e^{j\omega})}{\partial \theta}\begin{bmatrix}\partial G_{1,1} &\deemph{0}\\
                        \deemph{0}&\partial G_{2,2}\end{bmatrix}^{-1}\frac{\partial G(e^{j\omega})}{\partial \theta}\\
&=\var{\hat{G}_1(\omega)} + \var{\hat{G}_2(\omega)}.
\end{align}

@@

  Using this extension, the frequency range covered by $f_k$ can then be calculated as
    \begin{align}
      \fMin{k} &= \geomean{f_{k-1}}{f_k}\\
      \fMax{k} &= \geomean{f_{k+1}}{f_k}
    \label{eq:excitation:fRange}
    \text{.}
    \end{align}
  This range can be seen as the power-spectral density counterpart of the discrete spectrum relation \eqref{eq:excitation:nearestLines}.
  Consequently, both signals can be expected to behave in approximately the same way.

@@

\section{Simulations} \label{sec:excitation:simulation}
In the following set of simulations, we will study how the \gls{FRF} of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from \secref{sec:excitation:multisine}.
  \subsection{Setup}
  We consider second-order systems with an equal damping and with resonance frequencies $4$, $8$, $20$, $40$, $80$, $200$, $400$, $800$, $2000$ and $4000 \unit{Hz}$.
  Using the \MATLAB\ instruction \texttt{cheby1}, discrete-time equivalents of these systems are generated.
  These can be represented by a transfer function of the form:
  \begin{equation}
    G \left( z \right)\Big|_{\damping, \fR} =
       \frac{         b_2  z^{2} + b_1 z + b_0}%
            {\phantom{a_2} z^{2} + a_1 z + a_0}
  \text{.}
  \label{eq:excitation:secondOrderSystemDTidentifiable}
  \end{equation}

### 2016-04-21 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Lots of work on CH03
Uniform commands: part 1

Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. 
Unfortunately, the \gls{LPM} presented in \TODO{\secref{sec:nparam:trunc:theoryLPMandWindowing}} and in \citep{Schoukens2009LPM} does not estimate the \gls{DC} value of the \gls{FRF}, hence the subscript ``$\setminus\mathrm{DC}$'' in equation \eqref{eq:impRespiDFT}. 
Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. 
This limitation is lifted by developing a simple estimator of the mean value, presented below.

@@

\item
Determine the first time-instant $\truncTime$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
\begin{align}\label{eq:truncTimeExpFit}
\truncTime = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
\end{align}
where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found. This is discussed below. %(see the discussion below).
% The value of $\gamma$ to be used depends on the system. %$\gamma = 0.1$ was found to be a good rule of thumb.

@@

\subsection{Simulation Results}\label{sec:nparam:trunc:simResults}

@@

In \figref{fig:nparam:trunc:LPMvsTRunc} one observes the following:
\begin{itemize}
\item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$ compared to the non-truncated \gls{LPM}, is observed. %i.e. a decrease of the black crosses w.r.t.~the gray ones is observed.

>>>>

Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. 
Unfortunately, the \gls{LPM} presented in \secref{sec:nparam:LRM} and in \citep{Schoukens2009LPM} does not estimate the \gls{DC} value of the \gls{FRF}, hence the subscript ``$\setminus\mathrm{DC}$'' in equation \eqref{eq:impRespiDFT}. 
Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. 
This limitation is lifted by developing a simple estimator of the mean value, presented below.

@@

\item
Determine the first time-instant $\truncTime$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
\begin{align}\label{eq:truncTimeExpFit}
\truncTime = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
\end{align}
where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found. This is discussed below.

@@

\subsection{Simulation Results}
\label{sec:nparam:trunc:simResults}

@@

In \figref{fig:nparam:trunc:LPMvsTRunc} one observes the following:
\begin{itemize}
\item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$ compared to the non-truncated \gls{LPM}, is observed.

### 2016-04-21 ch03-lrm/lrm-paper.tex
Uniform commands: part 1

\subsection{The Local Rational Method}
The \gls{LRM} as first introduced by \citep{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
I.e. the \gls{LRM} procedure tries to minimize the equation error in
\begin{equation}
  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
  \text{,}
\end{equation}
for which the corresponding cost function is
\begin{equation}
  \LocalVector{\CostFunc{\LRM}}
  \isdef 
  \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
      \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
      \text{.}
\end{equation}
where $\LocalVector{V}$ is vector consisting of \gls{iid} complex normally distributed variables~\citep{Gallager2008} that each have a variance $\sigma_V^2$, i.e. the disturbing noise is assumed white over the local frequency window.
Equivalently, the last equation can be rewritten as a linear regression problem
\begin{equation}
  \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
\end{equation}
where $\LocalMatrix{K}$ is the so-called design matrix (or observation matrix):
\begin{align}
  \label{eq:nparam:designMatrix}
  \LocalMatrix{K} 
    & \isdef 
  \mat{
     \LocalMatrix{K}_A &
     \LocalMatrix{K}_B & 
     \LocalMatrix{K}_C
  }\\
  \LocalMatrix{K}_A 
    &\isdef
    \mat{
      \LocalVector{Y} \hadamard \LocalVector{d}^1 &
      \cdots &
      \LocalVector{Y} \hadamard \LocalVector{d}^{\numel{A}}
    }\\
  \LocalMatrix{K}_B 
    &\isdef
    \mat{
      \LocalVector{U} \hadamard \LocalVector{d}^0 &
      \cdots &
      \LocalVector{U} \hadamard \LocalVector{d}^{\numel{B}}
    }\\
  \LocalMatrix{K}_C
    &\isdef
    \mat{
      \LocalVector{d}^0 &
      \cdots &
      \LocalVector{d}^{\numel{C}}
    }\\
    \LocalVector{d}^{n} & \isdef
    \mat{
      (-\numel{W})^{n} &
      \cdots &
      (\numel{W})^{n}
    }^{\T}
    \text{ with $n \in \mathbb{Z}$.}
\end{align}
This formulation facilitates to solve the problem in a one-step approach:
\begin{equation}
  \LocalVector{\theta}_{\LRM} 
    \isdef \pinv{\LocalMatrix{K}} \LocalVector{Y}
    = \KTK{\LocalMatrix{K}} \LocalVector{Y}
\end{equation}
where $\pinv{\LocalMatrix{K}}$ denotes the Moore-Penroose pseudo-inverse of $\LocalMatrix{K}$.

@@

\TODO{plot example spectrums}
\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[Example spectra]
  \label{fig:nparam:spectra}
\end{figure}

@@

\begin{guideline}{For resonant systems, use the LRM when $\SNR \geq 20 \unit{dB}$}
\end{guideline}

\begin{guideline}{For long measurements, the choice of local modeling method does not matter}
\end{guideline}

@@

  \section{Conclusion}
  \label{sec:conclusion}

  \begin{itemize}
    \item LRM: extension to LRIC
    \item LRM: derivation of bias
    \item LRM vs LPM: at which settings is LRM better than LPM
    \item LRIC: much slower, performance is somewhat better, but at the cost of a lot of computational power and much harder model selection
    \item practical advice: use LRM rather than LPM unless in very noisy conditions (10 dB), only use LRIC as last resort
  \end{itemize}

>>>>

\subsection{The Local Rational Method}
\label{sec:nparam:LRM}
The \gls{LRM} as first introduced by \citep{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
I.e. the \gls{LRM} procedure tries to minimize the equation error in
\begin{equation}
  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
  \text{,}
\end{equation}
for which the corresponding cost function is
\begin{equation}
  \LocalVector{\CostFunc{\LRM}}
  \isdef 
  \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
      \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
      \text{.}
\end{equation}
where $\LocalVector{V}$ is vector consisting of \gls{iid} complex normally distributed variables~\citep{Gallager2008} that each have a variance $\sigma_V^2$, i.e. the disturbing noise is assumed white over the local frequency window.
Equivalently, the last equation can be rewritten as a linear regression problem
\begin{equation}
  \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
\end{equation}
where $\LocalMatrix{K}$ is the so-called design matrix (or observation matrix):
\begin{align}
  \label{eq:nparam:designMatrix}
  \LocalMatrix{K} 
    & \isdef 
  \mat{
     \LocalMatrix{K}_A &
     \LocalMatrix{K}_B & 
     \LocalMatrix{K}_C
  }\\
  \LocalMatrix{K}_A 
    &\isdef
    \mat{
      \LocalVector{Y} \hadamard \LocalVector{d}^1 &
      \cdots &
      \LocalVector{Y} \hadamard \LocalVector{d}^{\numel{A}}
    }\\
  \LocalMatrix{K}_B 
    &\isdef
    \mat{
      \LocalVector{U} \hadamard \LocalVector{d}^0 &
      \cdots &
      \LocalVector{U} \hadamard \LocalVector{d}^{\numel{B}}
    }\\
  \LocalMatrix{K}_C
    &\isdef
    \mat{
      \LocalVector{d}^0 &
      \cdots &
      \LocalVector{d}^{\numel{C}}
    }\\
    \LocalVector{d}^{n} & \isdef
    \mat{
      (-\numel{W})^{n} &
      \cdots &
      (\numel{W})^{n}
    }^{\T}
    \text{ with $n \in \mathbb{Z}$.}
\end{align}
This formulation facilitates to solve the problem in a one-step approach:
\begin{equation}
  \LocalVector{\theta}_{\LRM} 
    \isdef \pinv{\LocalMatrix{K}} \LocalVector{Y}
    = \KTK{\LocalMatrix{K}} \LocalVector{Y}
\end{equation}
where $\pinv{\LocalMatrix{K}}$ denotes the Moore-Penroose pseudo-inverse of $\LocalMatrix{K}$.

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOfig[Example spectra]
  \label{fig:nparam:spectra}
\end{figure}

@@

\begin{guideline}[Use the LRM when $\SNR \geq 20 \unit{dB}$ for resonant systems]
\end{guideline}

\begin{guideline}[Use the LPM when $\SNR \leq 20 \unit{dB}$]
\end{guideline}

\begin{guideline}[For long measurements, LPM and LRM are similar]
\end{guideline}

@@

### 2016-04-21 ch03-lrm/nonparametric.tex
Uniform commands: part 1

\begin{remark}
Unfortunately, these typical approaches either assume that an abundantly large dataset is available or  assume the models are estimated on  a fixed dataset.
As such, these methods are not ideal for local modeling where the (local) dataset is rather small by design and could change by means of the local bandwidth $N_W$.
\end{remark}

@@

>>>>

\begin{remark}
The typical approaches, such as the holdout and plug-in methods, either assume that an abundantly large dataset is available or  assume the models are estimated on a fixed dataset.
As such, these methods are not ideal for local modeling where the (local) dataset is rather small by design and could change by means of the local bandwidth $\nWind$ over the frequency.
\end{remark}

@@

  \section{Conclusion}
  \label{sec:conclusion}

  \begin{itemize}
    \item LRM: extension to LRIC
    \item LRM: derivation of bias
    \item LRM vs LPM: at which settings is LRM better than LPM
    \item LRIC: much slower, performance is somewhat better, but at the cost of a lot of computational power and much harder model selection
    \item practical advice: use LRM rather than LPM unless in very noisy conditions (10 dB), only use LRIC as last resort
  \end{itemize}

### 2016-04-21 ch04-lrmhinf/lrmhinf.tex
Uniform commands: part 1

The parametrization of the plant model set $\ModelSet[]$ conforms to the dual-\YK{} framework~\citep{Hansen1989,Anderson1998} that parametrizes $\ModelSet[]$ in terms of  all plants $P$ that are stabilized by the controller $C$:
\begin{equation}
  \ModelSet[] 
    \isdef 
      \Set{
            \frac{\hat{N} + D_c \Delta}
                 {\hat{D} - N_c \Delta} 
          |
            \hinfnorm{\Delta} \leq \gamma
        }
  \label{eq:lrmhinf:dualYoulaModelSet}
  \text{,}
\end{equation}
where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:lrmhinf:dualYoula}).
To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
These can be computed from $u$ and $y$ directly~\citep{Anderson1998}:
\begin{align}
  u_{\Delta}(t) &= \left(\hat{D} + C \hat{N} \right)^{-1} \mat{C & \I} \mat{y(t)\\u(t)}\\
  y_{\Delta}(t) &= \left(D_c + \hat{P} N_c \right)^{-1} \mat{\I & -\hat{P}} \mat{y(t)\\u(t)}
\end{align}
In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989} and uncorrelated to $y_{\Delta}$. 
Hence the method of \secref{sec:lrmhinf:LPMHinf} applies directly.

@@

\subsection{Results}
\label{sec:lrmhinf:resultsAvis}
To estimate $\Delta(\omega_k)$ and $\hinfnorm{\Delta}$  using the proposed approach with $\lrm{6,2,2,2}$, a short estimation dataset is used.
This estimation dataset is sampled from a larger dataset that contains four times more excited frequency lines (and hence produces a four times more densely sampled \gls{FRF}).
The full dataset, i.e. including the bins not seen during the estimation phase, is used to validate the interpolation results.

@@

This suggests that the local rational models with interpolation enable accurate estimation of  $\abs{\Delta}$ and hence also $\hinfnorm{\Delta}$ even if the actual peak does not coincide with the discrete frequency grid.

@@

The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a n accurate estimate of the $\Hinf{}$ norm.
It is observed that the measurement time is reduced by almost an order of magnitude compared to techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.
Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\hinfnorm{\Delta}$ and/or reduce the measurement time four-fold.
Furthermore, the results are validated by a detailed validation measurement.
Ongoing research focuses on extending the technique to \gls{MIMO} systems.

>>>>

The parametrization of the plant model set $\ModelSet[]$ conforms to the dual-\YK{} framework~\citep{Hansen1989,Anderson1998} that parametrizes $\ModelSet[]$ in terms of  all plants $P$ that are stabilized by the controller $C$:
\begin{equation}
  \ModelSet[] 
    \isdef 
      \Set{
            \frac{\hat{N} + D_c \Delta}
                 {\hat{D} - N_c \Delta} 
          |
            \infnorm{\Delta} \leq \gamma
        }
  \label{eq:lrmhinf:dualYoulaModelSet}
  \text{,}
\end{equation}
where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:lrmhinf:dualYoula}).
To estimate $\Delta$ and $\infnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
These can be computed from $u$ and $y$ directly~\citep{Anderson1998}:
\begin{align}
  u_{\Delta}(t) &= \left(\hat{D} + C \hat{N} \right)^{-1} \mat{C & \I} \mat{y(t)\\u(t)}\\
  y_{\Delta}(t) &= \left(D_c + \hat{P} N_c \right)^{-1} \mat{\I & -\hat{P}} \mat{y(t)\\u(t)}
\end{align}
In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989} and uncorrelated to $y_{\Delta}$. 
Hence the method of \secref{sec:lrmhinf:LPMHinf} applies directly.

@@

\subsection{Results}
\label{sec:lrmhinf:resultsAvis}
To estimate $\Delta(\omega_k)$ and $\infnorm{\Delta}$  using the proposed approach with $\lrm{6,2,2,2}$, a short estimation dataset is used.
This estimation dataset is sampled from a larger dataset that contains four times more excited frequency lines (and hence produces a four times more densely sampled \gls{FRF}).
The full dataset, i.e. including the bins not seen during the estimation phase, is used to validate the interpolation results.

@@

This suggests that the local rational models with interpolation enable accurate estimation of  $\abs{\Delta}$ and hence also $\infnorm{\Delta}$ even if the actual peak does not coincide with the discrete frequency grid.

@@

The technique is illustrated on a simulation example where the \gls{LRM}-based interpolation yields a n accurate estimate of the $\Hinf{}$ norm.
It is observed that the measurement time is reduced by almost an order of magnitude compared to techniques that only examine $\Delta(\omega)$ on the \gls{DFT} frequency grid.
Using measurements on an \gls{AVIS}, it is illustrated that the interpolation-based results can substantially improve $\infnorm{\Delta}$ and/or reduce the measurement time four-fold.
Furthermore, the results are validated by a detailed validation measurement.
Ongoing research focuses on extending the technique to \gls{MIMO} systems.
